Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.

### 2024-03-02 docs/_tex/index.tex
add disc
page layout

\includegraphics[width=0.5\textwidth,height=\textheight]{./Figures/Low_res/Compare_reflectance.png}

@@

In this study, a key innovation lies in the utilization of two different
altitudes (12m and 120m) for constructing the neural network model. The
lower altitude flights (8mm spatial resolution) enable precise selection
of pure pixels representing the classes used in the neural network
model. This methodology implies a consistency between the reflectance of
both altitude.

Figure~\ref{fig-CompareRef} depicts the relationship between reflectance
from a low-altitude flight and a high-altitude flight conducted over the
same area. An apparent underestimation of reflectance values is observed
in the high-altitude flight, particularly for higher values. Since both
flights were conducted over vegetation areas, the highest reflectance
values correspond to the infrared part of the spectrum. The disparity in
infrared reflectance may stem from temporal differences between the
flights, possibly resulting in a slightly drier intertidal area and
consequently higher infrared reflectance. This disparity poses an issue
for the methodology followed in the present study, relying solely on one
flight height for training. To address this issue, we employed min/max
standardized reflectance spectra as predictors for the model
(Equation~\ref{eq-std} ; \citep{Cao2017}). This approach allows us to
eliminate differences in the level of reflectance, focusing instead on
the shape of the spectra. This is a key feature in building a model that
can reliably predict vegetation across geographical sites and seasons.
It enables consistent prediction of vegetation classes across variations
in biomass and variability in light conditions \citetext{\citealp[
]{fyfe2003spatial}; \citealp[
]{COSTA2021107018}; \citealp{piaser2023impact}}.

@@

\section{Conclusion}\label{conclusion}

\renewcommand\refname{Bibliography}
  \bibliography{library.bib}

>>>>

\includegraphics[width=1\textwidth,height=\textheight]{./Figures/Low_res/Compare_reflectance.png}

@@

In this study, a key innovation lies in the utilization of two different
altitudes (12m and 120m) for constructing the neural network model. The
lower altitude flights (8mm spatial resolution) enable precise selection
of pure pixels representing the classes used in the neural network
model. This methodology implies a consistency between the reflectance of
both altitude. Figure~\ref{fig-CompareRef} depicts the relationship
between reflectance from a low-altitude flight and a high-altitude
flight conducted over the same area. An apparent underestimation of
reflectance values is observed in the high-altitude flight, particularly
for higher values. Since both flights were conducted over vegetation
areas, the highest reflectance values correspond to the infrared part of
the spectrum.

The disparity in infrared reflectance may stem from temporal differences
between the flights, possibly resulting in a slightly drier intertidal
area and consequently higher infrared reflectance. This disparity poses
an issue for the methodology followed in the present study, relying
solely on one flight height for training. To address this issue, we
employed min/max standardized reflectance spectra as predictors for the
model (Equation~\ref{eq-std} ; \citep{Cao2017}). This approach allows us
to eliminate differences in the level of reflectance, focusing instead
on the shape of the spectra. This is a key feature in building a model
that can reliably predict vegetation across geographical sites and
seasons. It enables consistent prediction of vegetation classes across
variations in biomass and variability in light conditions
\citetext{\citealp[ ]{fyfe2003spatial}; \citealp[
]{COSTA2021107018}; \citealp{piaser2023impact}}.

The Figure~\ref{fig-upscaling} demonstrates that a seagrass cover
percentage of 90 \% is necessary for confident prediction of seagrass
presence. This highlights a limitation of the methodology used to
construct the training dataset for the model. The dataset was composed
exclusively of pure pixels, which has resulted in the model's reduced
confidence when faced with lower percentages of seagrass cover. This
implies that outside of the biomass peak of seagrass this model should
be less accurate. This needs to be futher investigated.

@@

\renewcommand\refname{Conclusion}
  \bibliography{library.bib}

### 2024-03-02 index.qmd
add disc
page layout

::: columns
::: column
```{r Plot Reflectance_Validation 2 height}
#| cache: false
#| echo: false
#| warning: false
#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area. The red dashed line represents a linear model wheras the black dashed line represents a 1 to 1 relationship. 
#| label: fig-CompareRef
#| fig-width: 5
#| fig-height: 5
#| out-width: "50%"

@@

::: column
In this study, a key innovation lies in the utilization of two different altitudes (12m and 120m) for constructing the neural network model. The lower altitude flights (8mm spatial resolution) enable precise selection of pure pixels representing the classes used in the neural network model. This methodology implies a consistency between the reflectance of both altitude.
:::
:::

 @fig-CompareRef depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area. An apparent underestimation of reflectance values is observed in the high-altitude flight, particularly for higher values. Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum. The disparity in infrared reflectance may stem from temporal differences between the flights, possibly resulting in a slightly drier intertidal area and consequently higher infrared reflectance. This disparity poses an issue for the methodology followed in the present study, relying solely on one flight height for training. To address this issue, we employed min/max standardized reflectance spectra as predictors for the model (@eq-std ; [@Cao2017]). This approach allows us to eliminate differences in the level of reflectance, focusing instead on the shape of the spectra. This is a key feature in building a model that can reliably predict vegetation across geographical sites and seasons. It enables consistent prediction of vegetation classes across variations in biomass and variability in light conditions [@fyfe2003spatial ; @COSTA2021107018 ; @piaser2023impact].

@@

# Bibliography

>>>>

::: columns
::: column
```{r Plot Reflectance_Validation 2 height}
#| cache: false
#| echo: false
#| warning: false
#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area. The red dashed line represents a linear model wheras the black dashed line represents a 1 to 1 relationship. 
#| label: fig-CompareRef
#| fig-width: 10
#| fig-height: 10
#| out-width: "100%"

@@

::: column
In this study, a key innovation lies in the utilization of two different altitudes (12m and 120m) for constructing the neural network model. The lower altitude flights (8mm spatial resolution) enable precise selection of pure pixels representing the classes used in the neural network model. This methodology implies a consistency between the reflectance of both altitude. @fig-CompareRef depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area. An apparent underestimation of reflectance values is observed in the high-altitude flight, particularly for higher values. Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.
:::
:::

The disparity in infrared reflectance may stem from temporal differences between the flights, possibly resulting in a slightly drier intertidal area and consequently higher infrared reflectance. This disparity poses an issue for the methodology followed in the present study, relying solely on one flight height for training. To address this issue, we employed min/max standardized reflectance spectra as predictors for the model (@eq-std ; [@Cao2017]). This approach allows us to eliminate differences in the level of reflectance, focusing instead on the shape of the spectra. This is a key feature in building a model that can reliably predict vegetation across geographical sites and seasons. It enables consistent prediction of vegetation classes across variations in biomass and variability in light conditions [@fyfe2003spatial ; @COSTA2021107018 ; @piaser2023impact].

The @fig-upscaling demonstrates that a seagrass cover percentage of `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % is necessary for confident prediction of seagrass presence. This highlights a limitation of the methodology used to construct the training dataset for the model. The dataset was composed exclusively of pure pixels, which has resulted in the model's reduced confidence when faced with lower percentages of seagrass cover. This implies that outside of the biomass peak of seagrass this model should be less accurate. This needs to be futher investigated.

@@
